### 2018-02-11 Writing/Thesis/content/chapter-approach.tex
More writing & some meta data calcs
More writing
more writing

Approach of ranking classifier implementations here realized by two concepts, regression-based and preference-based ranking, which will be explained in detail. Also predicting predictive accuracy here. Thus target function of the form $meta features^n \rightarrow classifiers^m$.

% Theory of approach
Since the aim is to generate a ranking of classification algorithms, first, performance values of a number of classifiers are recorded on a few data sets. Then, meta features are computed for each data set. This is for training the ranking model. This generates a table that contains all necessary informatino for training both types of rankers. A ranking of the classifiers for a new instance is then achieved by computing the meta features for the data set and subsequently uing it to query the underlying model.

@@

>>>>

In this chapter the two alternatives which ar

\section{Theory}

Approach of ranking classifier implementations here realized by two concepts, regression-based and preference-based ranking, which will be explained in detail. Also predicting predictive accuracy here. Thus target function of the form $meta features^n \rightarrow classifiers^m$.
performance measure chosen predictive accuracy

% Theory of approach
Since the aim is to generate a ranking of classification algorithms, first, performance values of a number of classifiers are recorded on a few data sets. Then, meta features are computed for each data set. This is for training the ranking model. This generates a table that contains all necessary informatino for training both types of rankers. A ranking of the classifiers for a new instance is then achieved by computing the meta features for the data set and subsequently using it to query the underlying model.

@@

\section{Implementation}

META FEATURES USED!

for mann-whitney U apache commons implementation used with ties averaged and NaNs removed before
